TwinPeaks2018

### 2018-05-23 doc/ms.tex
Working on the doc

The prior is $\pi(\btheta)$ and the scalars are
$\left\{ f_i(\btheta) \right\}$
for $i \in \{1, 2, ..., M\}$. In most examples $M$ will be 2.
Consider a family of thresholded distributions, indexed by threshold
values $\bell=\left\{\ell_i\right\}$, proportional to
\begin{align}
p(\btheta; \bell) &\propto
    \pi(\btheta)
    \prod_{i=1}^M \mathds{1}\left(f_i(\btheta) > \ell_i\right).
\end{align}
The normalising constant is the probability in the `upper right corner'
(in 2D):
\begin{align}
X(\bell) &= \int_{f_i(\btheta) > \ell_i, \forall_i} \pi(\btheta) \, d\btheta
\end{align}

>>>>

The prior is $\pi(\btheta)$ and the scalars are
$f(\btheta)$ and $g(\btheta)$. Letting $x=f(\btheta)$ and $y=g(\btheta)$,
the implied prior for $x$ and $y$ will be written $\pi(x, y)$.

Consider a family of thresholded distributions, indexed by threshold
values $(x^*, y^*)$, given by
\begin{align}
p(x, y; x^*, y^*) &= \frac{\pi(x, y)\mathds{1}(x > x^*, y > y^*)}
                          {X(x^*, y^*)}
\end{align}
The normalising constant is the probability in the `upper right corner':
\begin{align}
X(x^*, y^*) &= \int_{y^*}^{\infty} \int_{x^*}^{\infty} \pi(x, y) \, dx \, dy.
\end{align}

The Kullback-Leibler divergence from the prior to a thresholded distribution
is
\begin{align}
D_{\rm KL}\left(p(x, y; x^*, y^*) \,||\, \pi(x, y)\right) &=
    \log X(x^*, y^*).
\end{align}

\section{Nested Sampling distribution}
Consider the following distribution:
\begin{align}
p_{\rm NS}(x, y) &= \frac{\pi(x, y)}{C X(x, y)}.
\end{align}
Compared to the prior $\pi$, this puts more weight at high values of
$x$ and $y$.

The KL divergence from $p_{\rm NS}$ to $p(x, y ; x^*, y^*)$ is
\begin{align}
D_{\rm KL}\left(p(x, y; x^*, y^*) \,||\, p_{\rm NS}(x, y)\right)
&=
\int_{y^*}^{\infty} \int_{x^*}^{\infty}
    \frac{\pi(x, y)}{X(x^*, y^*)}
    \log \left[\frac{C X(x, y)}{X(x^*, y^*)}\right]
    \, dx \, dy \\
&=
\frac{1}{X(x^*, y^*)}
\int_{y^*}^{\infty} \int_{x^*}^{\infty}
    \pi(x, y)
    \log \left[\frac{C X(x, y)}{X(x^*, y^*)}\right]
    \, dx \, dy \\
&=
\frac{\int_{y^*}^{\infty} \int_{x^*}^{\infty}
     \pi(x, y)
     \log \left[C X(x, y)\right]
     \, dx \, dy - X(x^*, y^*)\log X(x^*, y^*)}
     {X(x^*, y^*)}
\end{align}
